Precision calculations for cosmic shear

### 2017-02-09 cfhtlens.tex
MK small changes

We re-analyse the 2D CFHTLenS measurement of the two-point shear correlation
function $\xi_\pm(\theta)$ from \cite{CFHTLenS-2pt-notomo}, defined in
(\ref{eqn:xiGG}). As in \cite{CFHTLenS-2pt-notomo} we fit both components
$\xi_+$ and $\xi_-$ between angular scales $\theta = 0.8$ and $350$ arc
minutes, and use a $N$-body simulation estimate of the non-Gaussian covariance
including the cross-covariance between both components. The Bayesian
Monte-Carlo parameter sampling is performed using the publically available
software \textsc{CosmoPMC}\footnote{\texttt{www.cosmopmc.info}}
\citep{WK09,KWR10}. The cosmological modelling part including the various
lensing projections are performed with the library
\textsc{nicaea}\footnote{\texttt{http://www.cosmostat.org/software/nicaea}}.

>>>>

We re-analyse the 2D CFHTLenS measurement of the two-point shear correlation
function $\xi_\pm(\theta)$ from \cite{CFHTLenS-2pt-notomo}, defined in
(\ref{eqn:xiGG}). As in \cite{CFHTLenS-2pt-notomo} we fit both components
$\xi_+$ and $\xi_-$ between angular scales $\theta = 0.8$ and $350$ arc
minutes, and use a $N$-body simulation estimate of the non-Gaussian covariance
including the cross-covariance between both components. The Bayesian
Monte-Carlo parameter sampling is performed using the publically available
software \textsc{CosmoPMC}\footnote{\texttt{http://www.cosmostat.org/software/cosmopmc}}
\citep{WK09,KWR10}. The cosmological modelling part including the various
lensing projections are performed with the library
\textsc{nicaea}\footnote{\texttt{http://www.cosmostat.org/software/nicaea}}.
